Covariates analysis of MSBB RNASeq data

### 2016-05-18 code/Rmd/MSSM_RNASeq.Rmd
Minor modifications

# Arrange expression and covariates
COUNT = COUNT[, rownames(COVARIATES)]
```
Covariate correlation
```{r covariates.correlation, fig.width=10, fig.height=10}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
ggheatmap.show(COVARIATES.CORRELATION$plot, col.width=0.3, row.width=0.15)
```
### CPM Normalisation
Preprocess counts matrix and metadata. Determine design matrix for normalisation and differential expression analysis.

>>>>

# Arrange expression and covariates
COUNT = COUNT[, rownames(COVARIATES)]
```
Covariate correlation
```{r covariates.correlation, fig.width=10, fig.height=10}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
ggheatmap.show(COVARIATES.CORRELATION$plot, col.width=0.3, row.width=0.15)
```

```{r dataExplore, fig.width = 10, fig.height = 10}
# RIN
p = list()
p[[1]] = ggplot(METADATA, aes(x = Dx, y = RIN, fill = BrainRegion)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + theme(legend.position = 'top')

# AgeAtDeath
p[[2]] = ggplot(METADATA, aes(x = Dx, y = as.numeric(AOD), fill = BrainRegion)) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('AgeOfDeath') + theme(legend.position = 'top')

# Mean Plaque
p[[3]] = ggplot(METADATA, aes(x = Dx, y = as.numeric(PlaqueMean), fill = BrainRegion)) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PlaqueMean') + theme(legend.position = 'top')

# Mean Plaque
p[[4]] = ggplot(METADATA, aes(x = Dx, y = as.numeric(NP.1), fill = BrainRegion)) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('NP.1') + theme(legend.position = 'top')

multiplot(plotlist = p, cols = 2)

# Sex
vcd::mosaic(~ SEX + Dx + BrainRegion, data = METADATA)
```

### CPM Normalisation
Preprocess counts matrix and metadata. Determine design matrix for normalisation and differential expression analysis.
